\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black]{hyperref} % Links
\usepackage{makeidx} % Indexierung
\usepackage{siunitx}
\usepackage[ngerman]{babel} % deutsche Sonderzeichen
\usepackage[utf8]{inputenc}
\usepackage{geometry} % Dokumentendesign wie Seiten- oder Zeilenabstand bestimmen
\usepackage[toc,page]{appendix}

% Graphiken
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfcore}
\usepackage{pgfopts}
\usepackage{pgfornament}
\usepackage{pgf}
\usepackage{ifthen}
\usepackage{booktabs}

% Tabellen
\usepackage{tabu}
\usepackage{longtable}
\usepackage{colortbl} % Tabellen faerben
\usepackage{multirow}
\usepackage{diagbox} % Tabellenzelle diagonal splitten

\usepackage{xcolor} % Farben
\usepackage[framemethod=tikz]{mdframed} % Hintergrunderstellung
\usepackage{enumitem} % Enumerate mit Buchstaben nummerierbar machen
\usepackage{pdfpages}
\usepackage{listings} % Source-Code darstellen
\usepackage{eurosym} % Eurosymbol
\usepackage[square,numbers]{natbib}
\usepackage{here} % figure an richtiger Stelle positionieren
\usepackage{verbatim} % Blockkommentare mit \begin{comment}...\end{comment}
\usepackage{ulem} % \sout{} (durchgestrichener Text)

\usepackage{fontawesome}
\usepackage{titlesec}

% BibLaTex
\bibliographystyle{acm}

% Aendern des Anhangnamens (Seite und Inhaltsverzeichnis)
\renewcommand\appendixtocname{Anhang}
\renewcommand\appendixpagename{Anhang}

% mdframed Style
\mdfdefinestyle{codebox}{
	linewidth=2.5pt,
	linecolor=codebordercolor,
	backgroundcolor=codecolor,
	shadow=true,
	shadowcolor=black!40!white,
	fontcolor=black,
	everyline=true,
}

% Seitenabstaende
\geometry{left=10mm,right=10mm,top=5mm,bottom=5mm}

% TikZ Bibliotheken
\usetikzlibrary{
    arrows,
    arrows.meta,
    decorations,
    backgrounds,
    positioning,
    fit,
    petri,
    shadows,
    datavisualization.formats.functions,
    calc,
    shapes,
    shapes.multipart
}

\pgfplotsset{width=7cm,compat=1.15}

\definecolor{codecolor}{HTML}{EEEEEE}
\definecolor{codebordercolor}{HTML}{CCCCCC}

% Standardeinstellungen fuer Source-Code
\lstset{
    language=C,
    breaklines=true,
    keepspaces=true,
    keywordstyle=\bfseries\color{green!70!black},
    basicstyle=\ttfamily\color{black},
    commentstyle=\itshape\color{purple},
    identifierstyle=\color{blue},
    stringstyle=\color{orange},
    showstringspaces=false,
    rulecolor=\color{black},
    tabsize=2,
    escapeinside={\%*}{*\%},
}

\pagenumbering{gobble}

\def\CLOUD{cloud}
\def\HPC{hpc}

\setlength\parindent{0pt}

\titleformat{\section}{\large\bf\scshape\raggedright}{}{0em}{}
  [\titlerule]

\begin{document}

\begin{center}
  \textbf{\Large{Jonas Fassbender}} \\
\end{center}
\noindent
\begin{tabu} to \linewidth {lXlXl}
\faMapMarker \ Cologne, Germany
  &
  &\faHome \ \underline{\href{https://fassbender.dev}{fassbender.dev}}
  &
  & \faGithub \ \underline{\href{https://github.com/jofas}{jofas}}
  \\
\faPhone \ +49 1578 8286049
  &
  & \faLinkedin \ \underline{\href{https://www.linkedin.com/in/jofas}{jofas}}
  &
  & \faStackOverflow \ \underline{\href{https://stackoverflow.com/users/20665825/jonas-fassbender}{jonas-fassbender}}
  \\
\faEnvelope \ \underline{\href{mailto:jonas@fassbender.dev}{jonas@fassbender.dev}}
  &
  &
  &
  &
  \\
\end{tabu}

\section*{Synopsis}

Freelancing Software Engineer with 2+ years of experience building
enterprise applications and data pipelines.
Generalist with a broad range of interests.
I like trying out new technologies and feel at ease using them quickly.
Well versed in parallel and distributed computing techniques.
Concerned about software and API quality.
Enticed by Machine Learning.
FLOSS enthusiast.

\section*{Professional Experience}

\begin{itemize}[label={}, leftmargin=*]

\item \textbf{Oct 2020 -- now: Self-employed Software Engineer.}

  \begin{itemize}[label=\bullet, leftmargin=*]
    \item \textbf{German Sport University Cologne.}
      Created the technical domain specification for an
      application for teachers to conveniently generate rich semester
      plans that apply Inquiry-based Learning.
      Currently in the stage of raising funds for development.

    \item \textbf{\underline{\href{https://carpolice.de}{carpolice.de.}}}
      Developed second iteration of the carpolice.de Insurtech platform for car
      dealers, enabling them to sell car insurance products.
      Used by 300+ car dealers to sell 2k+ insurance policies.
      RESTful API-first microservice application written in Rust with
      a web client written in Dart/Flutter.
      Hosted on GKE.
      Used technologies include MongoDB, Redis, Elastic stack,
      Keycloak, ROOK/Ceph and OpenVPN.
      70k+ LoC.
      Launched in in April 2021 and retired in July 2023.

    \item \textbf{\underline{\href{https://fassbender.dev/static/cp_for_loan_approval_prediction.pdf}{%
        Improving the consumer loan approval process of a German bank using Machine Learning.}}}
      Applied a Conformal Prediction based classifier to pre-reject
      loan requests likely to be declined, saving the fee of querying
      a credit bureau.
      Able to pre-reject 17\% of all rejected requests while
      maintaining an accuracy of 98\%.
      Currently not applied in production.
  \end{itemize}

\item \textbf{Sep 2018 -- Jul 2019: Working Student, RLE International.}
In a team with other students, explored ways for RLE
International to adopt Machine Learning as an emerging technology and
create ML-powered products and solutions for customers.
Applied different ML-models to OEM ECRs (Engineering Change Requests)
of an automobile manufacturer, predicting how much time an ECR is
going to take to be resolved.

\item \textbf{Jul 2015 -- Aug 2016: Small Business System Administrator,
Lieb EDV Beratung.}
Set up and maintained backup systems and performed general
administration tasks on Windows servers and domains for several small
businesses.

\end{itemize}

\section*{FLOSS Contributions}

\begin{itemize}[label={}, leftmargin=*]

\item \textbf{Rust.} Creator and maintainer of
  \underline{\href{https://crates.io/users/jofas}{various Rust crates}}
  with 100k+ combined downloads from crates.io.
  \underline{\href{https://users.rust-lang.org/u/jofas/summary}{Regular}}
  on the Rust Users Forum with 100+ solutions.
  Occasional contributor to core Rust projects like
  \underline{\href{https://github.com/rust-lang/cargo}{Cargo}} and
  community projects like
  \underline{\href{https://github.com/actix/}{Actix}}.

\item \textbf{Personal Projects.} When I find the time and leisure I'm
  currently working on a fractal image generator called
  \underline{\href{https://github.com/jofas/mgart}{Mgart}}
  and a terminal-based bookkeeping tool I use for my work as
  freelancer (such as invoicing and time keeping) called
  \underline{\href{https://github.com/jofas/BAREKEEPER}{BAREKEEPER}}.

\item \textbf{Microcontributions.} Contributing fixes and enhancements
  to FLOSS projects I use whenever I find them.
  Most notable projects I've micro-contributed to in the past are
  \underline{\href{https://github.com/flutter/flutter}{Flutter's Material Design library}}
  and the
  \underline{\href{https://github.com/SpiNNakerManchester}{SpiNNaker Python frontends}}.

\end{itemize}

\section*{Education}

\begin{itemize}[label={}, leftmargin=*]

\item \textbf{Sep 2019 - Sep 2020: MSc High Performance Computing with Data
  Science, University of Edinburgh.} Thesis: Deep Learning on SpiNNaker

\item \textbf{Oct 2016 - Aug 2019: BSc Computer Science, Technical
  University of Cologne.} Thesis: Approximating the Optimal Threshold
  for an Abstaining Classifier based on a Reward Function with Regression

\end{itemize}

\section*{Technologies}

\begin{tabu} to \linewidth {lX}
Programming languages
& Rust, Dart, Python, JavaScript, Julia, C, Fortran \\
Web Development
& HTML, CSS, tailwind, REST, GraphQL, Actix Web \\
Cloud Computing
& Kubernetes, Docker, Google Cloud Platform, Elastic Cloud on
  Kubernetes, cert-manager, NGINX Ingress Controller, ROOK/Ceph, Firebase \\
Data Science
& scikit-learn, Keras, Tensorflow, numpy, polars, Matplotlib \\
Others
& Flutter, OpenID Connect, Keycloak, Git, {\LaTeX}, OpenSUSE/Linux, Bash, SQL,
  MongoDB, Redis, Elastic stack, RabbitMQ, Kafka, MPI, OpenMP \\
\end{tabu}

\end{document}
